RationalGRL: A Framework for Argumentation and Goal Modeling

### 2017-09-13 transcripts.tex
Section 4 (RationalGRL Framework)

\begin{table}[!htbp]
\centering
\begin{tabular}{|p{17mm}|p{63mm}|p{70mm}|}
\hline
\textit{Speaker} & \textit{Text} & \textit{Annotation}\\
\hline
(P1) & And then, we have a set of actions. Save map, open map, add and remove intersection, roads & \multirow{2}{70mm}{\textbf{[20 task (AS2)]} Student has tasks ``save map'', ``open map", ``add intersection", ``remove intersection", ``add road", ``add traffic light" \textsf{[INTRO]}}\\
\cline{1-2}
(P2) & Yeah, road. Intersection, add traffic lights &\\
\hline
(P1) & Well, all intersection should have traffic lights so it's & \multirow{4}{70mm}{\textbf{[21 critical question CQ12 for 20]} Is the task ``Add traffic light" useful/relevant?\newline
\textbf{[22 answer to 21]} Not useful, because according to the specification all intersections have traffic lights. \textsf{[ATTACK]}}\\
\cline{1-2}
(P2) & Yeah &\\
\cline{1-2}
(P1) & It's, you don't have to specifically add a traffic light because if you have &\\
\cline{1-2}
(P2)	& They need-&\\
\hline
\end{tabular}
\caption{Adding tasks, disabling useless task ``Add traffic light'' (transcript $t_1$)}
\label{table:transcripts:traffic-light}

\begin{tabular}{|p{17mm}|p{63mm}|p{70mm}|}
\hline
\textit{Speaker} & \textit{Text} & \textit{Annotation}\\
\hline
0:17:39 (P1) & And in that process there are activities like create a visual map, create a road& \textbf{[14 task (AS2)]} Student has task ``Create road'' \textsf{[INTRO]}\\
\hline
0:24:36.0 (P3)	& And, well interaction. Visualization sorry. Or interaction, I don't know. So create a visual map would have laying out roads and a pattern of their choosing. So this would be first, would be choose a pattern. & \textbf{[31 critical question CQ13 for 14]} Is Task ``Create road'' clear?\newline
\textbf{[32a answer to 31]} no, according to the specification the student should choose a pattern. \newline
\textbf{[32b answer to 31]} ``Create road'' becomes ``Choose a pattern'' \textsf{[REPLACE]}\\
\hline
0:24:55.4 (P1) &	How do you mean, choose a pattern	& \textbf{[33 critical question CQ13 for 32b]} Is ``Choose a pattern'' clear? \\
\cline{1-2}
0:24:57.5 (P3)	& Students must be able to create a visual map of an area, laying out roads in a pattern of their choosing	&\\
\cline{1-2}
0:25:07.5 (P1)	& Yeah I'm not sure if they mean that. I don't know what they mean by pattern in this case. I thought you could just pick roads, varying sizes and like, broads of roads. & 
\textbf{[34a answer to 33]} No, not sure what they mean by a pattern.\\
\cline{1-2}
0:25:26.0 (P3) & No yeah exactly, but you would have them provide, it's a pattern, it's a different type of road but essentially you would select- how would you call them, selecting a- & \multirow{3}{70mm}{\textbf{[34b answer to 33]} ``Choose a pattern'' becomes ``Choose a pattern preference'' \textsf{[REPLACE]}}\\
\cline{1-2}
0:25:36.3 (P1) & Yeah, selecting a- I don't know &\\
\cline{1-2}
0:25:38.0 (P3)	& Pattern preference maybe? As in, maybe we can explain this in the documentation &\\
\hline
0:25:43.9 (P1) & What kind of patterns though. Would you be able to select & \textbf{[35 critical question CQ13 for 34b]} Is ``Choose a pattern preference'' clear?\newline
\textbf{[36a answer to 35]} no, what kind of pattern?\\
\cline{1-2}
0:25:47.4 (P3) & Maybe, I don't know it's- & \\
\cline{1-2}
0:25:48.5 (P1)	& [inaudible] a road pattern& \multirow{2}{70mm}{\textbf{[36b answer to 35]} ``Choose a pattern preference'' becomes ``Choose a road pattern'' \textsf{[REPLACE]}}\\
\hline
\end{tabular}
\caption{Clarifying the name of a task (transcript $t_3$)}
\label{table:transcript:task-clarification}

\begin{tabular}{|p{17mm}|p{43mm}|p{90mm}|}
\hline
\textit{Speaker} & \textit{Text} & \textit{Annotation}\\
\hline
0:18:55.7 (P1) &Yeah. And then two processes, static, dynamic and they belong to the goal simulate. & \textbf{[17 goal (AS3)]} System has goal ``Simulate'' \textsf{[INTRO]}\newline
\textbf{[18 task (AS2)]} System has tasks ``Static simulation'', ``Dynamic simulation'' \textsf{[INTRO]}\newline  
\textbf{[20 decomposition (AS5)]} Goal ``Simulation" AND-decomposes into "Static simulation" and ``Dynamic simulation" \textsf{[INTRO]}\\
\hline
0:30:10.3 (P1) & 	Yeah. But this is- is this an OR or an AND? & \multirow{5}{80mm}{\textbf{[26 critical question CQ10b for 20]} Is the decomposition type of ``simulate'' correct?\newline
\textbf{[27 answer to 26]} No, it should be an OR decomposition. \textsf{[REPLACE]}}\\
\cline{1-2}
0:30:12.6 (P2) & That's and OR &\\
\cline{1-2}
0:30:14.3 (P3) & I think it's an OR &\\
\cline{1-2}
0:30:15.4 (P1) & It's for the data, it's an OR &\\
\cline{1-2}
0:30:18.1 (P3) & Yep &\\
\hline	
\end{tabular}
\caption{Incorrect decomposition type for goal \emph{Simulate} (transcript $t_3$)}
\label{table:transcript:decomposition}
\end{table}

>>>>

\begin{table}[!htbp]
\centering
\begin{tabular}{|p{17mm}|p{63mm}|p{70mm}|}
\hline
\textit{Speaker} & \textit{Text} & \textit{Coding}\\
\hline
0:15:11 (P1) & And then, we have a set of actions. Save map, open map, add and remove intersection, roads & \multirow{2}{70mm}{\textbf{[20 task (AS2)]} Student has tasks ``save map'', ``open map", ``add intersection", ``remove intersection", ``add road", ``add traffic light" \textsf{[INTRO]}}\\
\cline{1-2}
0:15:34 (P2) & Yeah, road. Intersection, add traffic lights &\\
\hline
0:15:42 (P1) & Well, all intersection should have traffic lights so it's & \multirow{4}{70mm}{\textbf{[21 critical question CQ12 for 20]} Is the task ``Add traffic light" useful/relevant?\newline
\textbf{[22 answer to 21]} Not useful, because according to the specification all intersections have traffic lights. \textsf{[ATTACK]}}\\
\cline{1-2}
0:15:44 (P2) & Yeah &\\
\cline{1-2}
0:15:45 (P1) & It's, you don't have to specifically add a traffic light because if you have &\\
\cline{1-2}
(P2)	& They need-&\\
\hline
\end{tabular}
\caption{Adding tasks, disabling useless task ``Add traffic light'' (transcript $t_1$)}
\label{table:transcripts:traffic-light}

\begin{tabular}{|p{17mm}|p{63mm}|p{70mm}|}
\hline
\textit{Speaker} & \textit{Text} & \textit{Coding}\\
\hline
0:17:39 (P1) & And in that process there are activities like create a visual map, create a road& \textbf{[14 task (AS2)]} Student has task ``Create road'' \textsf{[INTRO]}\\
\hline
0:24:36 (P3)	& And, well interaction. Visualization sorry. Or interaction, I don't know. So create a visual map would have laying out roads and a pattern of their choosing. So this would be first, would be choose a pattern. & \textbf{[31 critical question CQ13 for 14]} Is Task ``Create road'' clear?\newline
\textbf{[32a answer to 31]} no, according to the specification the student should choose a pattern. \newline
\textbf{[32b answer to 31]} ``Create road'' becomes ``Choose a pattern'' \textsf{[REPLACE]}\\
\hline
0:24:55 (P1) &	How do you mean, choose a pattern	& \textbf{[33 critical question CQ13 for 32b]} Is ``Choose a pattern'' clear? \\
\cline{1-2}
0:24:57 (P3)	& Students must be able to create a visual map of an area, laying out roads in a pattern of their choosing	&\\
\cline{1-2}
0:25:07 (P1)	& Yeah I'm not sure if they mean that. I don't know what they mean by pattern in this case. I thought you could just pick roads, varying sizes and like, broads of roads. & 
\textbf{[34a answer to 33]} No, not sure what they mean by a pattern.\\
\cline{1-2}
0:25:26 (P3) & No yeah exactly, but you would have them provide, it's a pattern, it's a different type of road but essentially you would select- how would you call them, selecting a- & \multirow{3}{70mm}{\textbf{[34b answer to 33]} ``Choose a pattern'' becomes ``Choose a pattern preference'' \textsf{[REPLACE]}}\\
\cline{1-2}
0:25:36 (P1) & Yeah, selecting a- I don't know &\\
\cline{1-2}
0:25:38 (P3)	& Pattern preference maybe? As in, maybe we can explain this in the documentation &\\
\hline
0:25:43 (P1) & What kind of patterns though. Would you be able to select & \textbf{[35 critical question CQ13 for 34b]} Is ``Choose a pattern preference'' clear?\newline
\textbf{[36a answer to 35]} no, what kind of pattern?\\
\cline{1-2}
0:25:47 (P3) & Maybe, I don't know it's- & \\
\cline{1-2}
0:25:48 (P1)	& [inaudible] a road pattern& \multirow{2}{70mm}{\textbf{[36b answer to 35]} ``Choose a pattern preference'' becomes ``Choose a road pattern'' \textsf{[REPLACE]}}\\
\hline
\end{tabular}
\caption{Clarifying the name of a task (transcript $t_3$)}
\label{table:transcript:task-clarification}

\begin{tabular}{|p{17mm}|p{43mm}|p{90mm}|}
\hline
\textit{Speaker} & \textit{Text} & \textit{Coding}\\
\hline
0:18:55 (P1) &Yeah. And then two processes, static, dynamic and they belong to the goal simulate. & \textbf{[17 goal (AS3)]} System has goal ``Simulate'' \textsf{[INTRO]}\newline
\textbf{[18 task (AS2)]} System has tasks ``Static simulation'', ``Dynamic simulation'' \textsf{[INTRO]}\newline  
\textbf{[20 decomposition (AS5)]} Goal ``Simulation" AND-decomposes into "Static simulation" and ``Dynamic simulation" \textsf{[INTRO]}\\
\hline
0:30:10 (P1) & 	Yeah. But this is- is this an OR or an AND? & \multirow{5}{80mm}{\textbf{[26 critical question CQ10b for 20]} Is the decomposition type of ``simulate'' correct?\newline
\textbf{[27 answer to 26]} No, it should be an OR decomposition. \textsf{[REPLACE]}}\\
\cline{1-2}
0:30:12 (P2) & That's and OR &\\
\cline{1-2}
0:30:14 (P3) & I think it's an OR &\\
\cline{1-2}
0:30:15 (P1) & It's for the data, it's an OR &\\
\cline{1-2}
0:30:18 (P3) & Yep &\\
\hline	
\end{tabular}
\caption{Incorrect decomposition type for goal \emph{Simulate} (transcript $t_3$)}
\label{table:transcript:decomposition}
\end{table}
